### 2013-11-22 tests_Housing.Rmd
added 2nd version of regularization
FC suggestion: make a more standard regularization: add to the rsme the
sum of the squared weigths (of the linear regression)

########################################################
# Lambda Test
lambda.values <- seq(0.5,0.999,length.out=20)
n.runs <- 5

@@

library(ggplot2)
qplot(lambda,error,data=df,geom=c("jitter","boxplot")) + 
  ylab("root-mean-square error") + 
  xlab("lambda value") +
 # coord_cartesian(ylim = c(0, 50))  +
  ggtitle("Housing dataset")
##############################################
# Check fitness progress

>>>>

########################################################
# Lambda Test (1st variant of regularization)
lambda.values <- seq(0.5,0.999,length.out=20)
n.runs <- 5

@@

library(ggplot2)
qplot(lambda,error,data=df,geom=c("jitter","boxplot")) + 
  ylab("root-mean-square error") + 
  xlab("lambda value") +
 # coord_cartesian(ylim = c(0, 50))  +
  ggtitle("Housing dataset")

########################################################
# Lambda Test (2nd variant of regularization)
size <- 31
lambda.values <- rep(NA, size)

val <- 0.001
for(i in 1:size) {
  lambda.values[i] = val
  val = val * 2^(1/3)  # duplicate every three steps
}

n.runs <- 5

source("gapolyfuncs.R")
errors <- test.lambda(my.data, lambda.values, runs=n.runs, population=5, iterations=15)

library(ggplot2)
qplot(lambda,error,data=df,geom=c("jitter","boxplot")) + 
  ylab("root-mean-square error") + 
  xlab("lambda value") +
 # coord_cartesian(ylim = c(0, 50))  +
  ggtitle("Housing dataset")

##############################################
# Check fitness progress
